251 MA

### 2023-03-08 code/process.Rmd
fussing

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point() +
  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = 1, 
                      name = "Subjective\nReplication\nSuccess\n")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "right")

@@

```{r}
sub_cor <- function(var, stat = "estimate") {
  if (stat == "estimate") {
    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$estimate
  } else {
    cor.test(data_tier1$sub_rep, pull(data_tier1, {{var}}))$p.value
  }
}

preds <- c("z_pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
           "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
           "z_log_trials")

cors <- tibble(preds = preds) |>
  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
         p = sapply(preds, function(x) sub_cor(x, stat = "p")))

knitr::kable(cors, digits = 3)
```

@@

ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none", axis.text=element_text(size=11))+labs(y="Count", x="Subjective Replication score")

@@

ggplot(dat, aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())

@@

dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))

@@

 ggplot(dat, aes(x=ifelse(stanford, "Stanford affiliation", "No Stanford affiliation"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())

 ggsave(here("plots/stanford.pdf"))

ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())

@@

ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))

@@

ggplot(dat, aes(x=ifelse(single_vignette, "1 vignette", "multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.title.x=element_blank())+theme( axis.text=element_text(size=11))

@@

>>>>

```{r}
d_es_predInt |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+

  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
   geom_point(size=2.5) +
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = 1, 
                      name = "Subjective\nReplication\nSuccess\n")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "right")

@@

```{r}
for_cor <- data_tier1 |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0)) 
sub_cor <- function(var, stat = "estimate") {
  if (stat == "estimate") {
    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$estimate
  } else {
    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$p.value
  }
}

preds <- c("z_pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
           "z_log_ratio_ss", "is_within", "single_vignette", "z_log_sample", 
           "z_log_trials", "social", "other_psych", "non_psych")

cors <- tibble(preds = preds) |>
  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(Predictors) |> select(Predictors, r, p)

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2", font_size=40) 
```

@@

ggplot(dat, aes(x=sub_rep, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(legend.position = "none", axis.text=element_text(size=14), axis.title=element_text(size=14))+labs(y="Count", x="Subjective Replication score")

@@

dat |> mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |> ggplot(aes(x=subfield, fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")

@@

dat |> mutate(open_mat=ifelse(open_mat, "Open materials", "No open materials"), open_data=ifelse(open_data, "Open data", "No open data")) |> ggplot( aes(x=open_data |> factor(), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+facet_wrap(.~open_mat)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), strip.text = element_text(size=14))+labs(y="Count")

@@

 # ggplot(dat, aes(x=ifelse(stanford, "Stanford affiliation", "No Stanford affiliation"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme( axis.text=element_text(size=11), axis.title.x=element_blank())
 # ggsave(here("plots/stanford.pdf"))

ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")

@@

ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")

@@

ggplot(dat, aes(x=ifelse(single_vignette, "Single vignette", "Multiple vignettes"), fill=sub_rep))+geom_bar(stat="count", position="dodge")+scale_fill_viridis(discrete=T)+theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+labs(y="Count")

@@

# d_for_model |> filter(!is.na(predInt)) |>  mutate(porig.num=ifelse(p_orig>.05, 1,0))|> summarize(pred=mean(predInt), por=mean(p_orig), pornum=mean(porig.num))
